---
title: "Hebrew CDI Longitudinal Growth
# Analyses for Gendler-Shalev, Marchman & Dromi (2025). Trajectories of early vocabulary growth in Hebrew-speaking toddlers: The role of comprehension"
output: html_document
date: '2022-08-23; updated 2022-10-5; submitted 2024-05-21; updated for revised version: 2025-05-15; Final: 2025-09-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load libraries
```{r}

library(tidyverse)
library(effsize)
library(stargazer)
library(psych)
library(reghelper)
library(lme4)
library(lmerTest)
library(dplyr)
library(ggplot2)
library(sjPlot) #for plotting lmer and glmer mods
library(effects)
library(sjmisc)
library(sjstats) #use for r2 functions
library(gamlss)
library(ggeffects)
library(emmeans)

```
#Load data.frame
```{r}

# Language was originally TD vs. LT, but in response to reviewers, language changed to "higher" vs. "lower";
# Comprehension levels also changed to "higher" vs. "lower"

Hebgrowth <- read.csv("HebGrowth_data.csv", header = TRUE) %>%
    mutate(LTgroup = case_when(
              LTgroup == 0 ~ "Higher",
              LTgroup == 1 ~ "Lower"),
           compptile_lev25 = case_when(
             compptile_lev25 == "high" ~ "Higher",
             compptile_lev25 == "low" ~ "Lower"),
           compptile_lev50 = case_when(
             compptile_lev50 == "high" ~ "Higher",
             compptile_lev50 == "low" ~ "Lower"),
           Sex = case_when(
             Sex == "1" ~ "M",
             Sex == "2" ~ "F"))
           
Hebgrowth$LTgroup <- factor(Hebgrowth$LTgroup, levels = c("Higher", "Lower"))

Hebgrowth$Sex <- factor(Hebgrowth$Sex, levels = c("M", "F"))

Hebgrowth$adm <- factor(Hebgrowth$adm, levels = c("1", "2", "3"))
         
```
#Table 1 and other descriptives
```{r}

Hebgrowth %>% 
  count(LTgroup)

Hebgrowth %>% group_by(adm, Sex) %>%
  count(AGE)

Hebgrowth %>% group_by(adm) %>%
  count(LTgroup)

# Table 1
Hebgrowth %>% filter(adm == "1") %>%
  group_by(adm, Sex, LTgroup) %>%
  count(AGE)

# comprehension vocabulary groups: 25th percentile at admin 1
Hebgrowth %>% filter(adm == "1") %>%
  group_by(adm) %>%
  count(compptile_lev25)

# comprehension vocabulary groups: 50th percentile at admin 1
Hebgrowth %>% filter(adm == "1") %>% 
  group_by(adm) %>%
  count(compptile_lev50)

```

#Table 2. Descriptives of prod and comp raw score by LT group at First administration
```{r}

Hebgrowth_adm1 <- Hebgrowth %>% group_by(LTgroup, adm) %>%
  filter(adm == "1")

Hebgrowth_desc_prodcomp <- Hebgrowth_adm1 %>% group_by(LTgroup) %>%
  dplyr::summarize(
    n = n(),
    Mean_Age = mean(AGE),
    SD_Age = sd(AGE),
    Min_Age = min(AGE),
    Max_Age = max(AGE),
    TotProd = mean(prod),
    SD_prod = sd(prod),
    TotComp = mean(Comp),
    SD_comp = sd(Comp),
  )

knitr::kable(
 Hebgrowth_desc_prodcomp,
  caption = "Table 2. Descriptive statistics for Production and Comprehension Raw Scores by group at first administration.",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

#group comparisons in prod and comp at adm1
t.test(prod ~ LTgroup, data = Hebgrowth_adm1)
effsize::cohen.d(Hebgrowth_adm1$prod, Hebgrowth_adm1$LTgroup)

t.test(Comp ~ LTgroup, data = Hebgrowth_adm1)
effsize::cohen.d(Hebgrowth_adm1$Comp, Hebgrowth_adm1$LTgroup)


```
#Table 3. Descriptives of prod and comp percentile scores by LT group and administration
```{r}

Hebgrowth_desc_prodcompptile <- Hebgrowth %>% 
  group_by(LTgroup, adm) %>%
  dplyr::summarize(
    n = n(),
    TotProdper = mean(prod_centile_rank),
    SD_prodp = sd(prod_centile_rank),
    Min_prodp = min(prod_centile_rank),
    Max_prodp = max(prod_centile_rank),
    TotCompper = mean(comp_centile_rank),
    SD_compp = sd(comp_centile_rank),
    Min_compp = min(comp_centile_rank),
    Max_compp = max(comp_centile_rank)
  )

knitr::kable(
 Hebgrowth_desc_prodcompptile,
  caption = "Table 3. Descriptive statistics for Production and Comprehension Percentiles by adm and group.",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

```

##Cross-tabs of prod percentile levels
```{r}

Hebgrowth %>% filter(adm == "1") %>%
  group_by(LTgroup, prod_centile_lev_adm2, prod_centile_lev_adm3) %>%
  count()

```
##Explore mean percentiles by change in 2nd and 3rd administration
```{r}

admin_status <- Hebgrowth %>% filter(adm == "1") %>%
  group_by(LTgroup, prod_centile_lev_adm2, prod_centile_lev_adm3) %>%
    dplyr::summarize(
    n = n(),
    TotProdper = mean(prod_centile_rank),
    SD_prodp = sd(prod_centile_rank),
    Min_prodp = min(prod_centile_rank),
    Max_prodp = max(prod_centile_rank),
    TotCompper = mean(comp_centile_rank),
    SD_compp = sd(comp_centile_rank),
    Min_compp = min(comp_centile_rank),
    Max_compp = max(comp_centile_rank)
  )

knitr::kable(
  admin_status,
  caption = "Mean Production and Comprehension Percentiles by Time 2 and 3 status",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

Hebgrowth_status <- Hebgrowth %>% filter(adm == "1", LTgroup == "Lower") %>%
 mutate(admin_group = case_when(prod_centile_lev_adm2 == 0 & prod_centile_lev_adm3 == 0 ~ 0,
                                prod_centile_lev_adm2 == 0 & prod_centile_lev_adm3 == 1 ~ 1,
                                prod_centile_lev_adm2 == 1 & prod_centile_lev_adm3 == 1 ~ 2))


Hebgrowth_status_desc <- Hebgrowth_status %>% filter(adm == "1") %>%
  group_by(admin_group) %>%
    dplyr::summarize(
    n = n(),
    TotProdper = mean(prod_centile_rank),
    SD_prodp = sd(prod_centile_rank),
    Min_prodp = min(prod_centile_rank),
    Max_prodp = max(prod_centile_rank),
    TotCompper = mean(comp_centile_rank),
    SD_compp = sd(comp_centile_rank),
    Min_compp = min(comp_centile_rank),
    Max_compp = max(comp_centile_rank)
  )

knitr::kable(
  Hebgrowth_status_desc,
  caption = "Mean Production and Comprehension Percentiles by admin status",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

status <- lm(prod_centile_rank ~ admin_group, data = Hebgrowth_status)

anova(status)

```

##Descriptives of comp percentile scores by LTgroup - 25th percentile

```{r}

# checking to make sure that group 1 compptile_lev25 is correct for all admins

Hebgrowth %>% group_by(adm) %>%
  count(compptile_lev25)

# checking to make sure that group 1 compptile_lev (50th percentile) is correct for all admins

Hebgrowth %>% group_by(adm) %>%
  count(compptile_lev50)

```
#Expressive vocabulary by LT/TD group over age
```{r}

# Note GAMLSS models are specifically using the "beta" distribution family, which means they are bounded by 0 and 1 (like a logistic)

Hebgrowth_gam <- Hebgrowth %>%
  mutate(prop_produced = as.numeric(prod/428))

#test to delete outlier - because results were the same with and without outlier, final models keep in all data
Hebgrowth_gam <- Hebgrowth %>% filter(CHILD_ID != 981) %>%
  mutate(prop_produced = as.numeric(prod/428))

Hebgrowth_gam <-Hebgrowth_gam %>%
  mutate(prop_produced = case_when(prop_produced == 0 ~ 0.001, 
                             prop_produced == 1 ~ 0.999,
                             TRUE ~ prop_produced))

#model 1 - age only

gam_age <- gamlss(prop_produced ~ pb(AGE, lambda = 10000),
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE,  
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

#model 2 - age and group main effects

gam_age_group <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

# model 3 - age and group main effects and interaction

gam_age_group_int <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup * pb(AGE, lambda = 10000),
                  sigma.formula = ~pb(AGE, lamda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

## Get summaries of models

summary(gam_age)
summary(gam_age_group)
summary(gam_age_group_int)

```
## Compare models using liklihood ratio test
```{r}
LR.test(gam_age, gam_age_group)
LR.test(gam_age_group, gam_age_group_int)

```
##Get model fit values
```{r}

# Get AIC values

AIC(gam_age)
AIC(gam_age_group)
AIC(gam_age_group_int)

# Get BIC values

BIC(gam_age)
BIC(gam_age_group)
BIC(gam_age_group_int)

# Get Rsquared values

Rsq(gam_age)
Rsq(gam_age_group)
Rsq(gam_age_group_int)

```
## Get predicted values at 12, 18 and 24 months
```{r}

group12 <- predict(gam_age_group, newdata = data.frame(AGE= 12, LTgroup=c("Higher", "Lower")), type = ("response"), re.form = ~0)

group12 <- group12 * 428
group12

group18 <-  predict(gam_age_group, newdata = data.frame(AGE= 18, LTgroup=c("Higher", "Lower")), type = "response", re.form = ~0)

group18 <- group18 * 428
group18

group24 <- predict(gam_age_group, newdata = data.frame(AGE= 24, LTgroup=c("Higher", "Lower")), type = "response", re.form = ~0)

group24 <- group24 * 428
group24

```
## Plot model results - main effects only model (Model 2)
```{r}

# Get predicted values and SE

predict_gam_age_group <- predict(gam_age_group, type = "response", se.fit = TRUE)

Hebgrowth_gam$fitted <- predict_gam_age_group$fit * 428
Hebgrowth_gam$se <- predict_gam_age_group$se.fit * 428

ggplot(Hebgrowth_gam, aes(y = fitted, x = AGE, linetype = LTgroup)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  geom_line(size = 1.1) +
  scale_color_manual(values=c("Grey", "Black")) +
  #geom_point(aes(y = prod, shape = compptile_lev25, color = LTgroup), show.legend = F) +
  #geom_jitter() +
  geom_ribbon(aes(ymin = fitted - se, ymax = fitted + se), fill = "grey", alpha = 0.5) +
  scale_shape_manual(values = c(16, 21)) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=seq(12,24,1)) +
  ylim(0,375) +
  labs(
    x = "Age in months", 
    y = "Words \n produced \n (modeled \n estimate)", linetype = "Expressive \nVocabulary \nGroup") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) +
  theme(text = element_text(size = 16))
  
ggsave("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper/growthplot_R1.jpg", height = 8, width = 11, units = "in", dpi = 300)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#Add main effect of comp (25th) to age and group (model 4)
```{r}

gam_age_group_comp25 <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev25,
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  random = ~ 1 | CHILD_ID, 
                  data = Hebgrowth_gam)

summary(gam_age_group_comp25)

```
##Add age x comp, group x comp interactions (Model 5) 
```{r}

gam_age_group_comp25_ageint <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev25 + pb(AGE, lambda = 10000) * LTgroup + pb(AGE, lambda = 10000) * compptile_lev25 + LTgroup * compptile_lev25,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

summary(gam_age_group_comp25_ageint)

gam_age_group_comp25_3way <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev25 + pb(AGE, lambda = 10000) * compptile_lev25 + LTgroup * compptile_lev25 + pb(AGE, lambda = 10000) * LTgroup * compptile_lev25,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

summary(gam_age_group_comp25_3way)

```
## Compare models using liklihood ratio test
```{r}
LR.test(gam_age_group, gam_age_group_comp25)
LR.test(gam_age_group_comp25, gam_age_group_comp25_ageint)
LR.test(gam_age_group_comp25, gam_age_group_comp25_3way)

```
##Get model fit values
```{r}

AIC(gam_age_group_comp25)
AIC(gam_age_group_comp25_ageint)
AIC(gam_age_group_comp25_3way)

# Get BIC values

BIC(gam_age_group_comp25)
BIC(gam_age_group_comp25_ageint)
BIC(gam_age_group_comp25_3way)

# Get Rsquared values

Rsq(gam_age_group_comp25)
Rsq(gam_age_group_comp25_ageint)
Rsq(gam_age_group_comp25_3way)
```
##Get predicted values by LT/TD group and comp (25th) at 18 and 24 months
```{r}

comp25_18_high <- predict(gam_age_group_comp25, newdata = data.frame(AGE= 18, LTgroup=c("TD", "LT"), compptile_lev25=c("high")), type = "response", re.form = ~0)

comp25_18_high <- comp25_18_high * 428
comp25_18_high

comp25_18_low <- predict(gam_age_group_comp25, newdata = data.frame(AGE= 18, LTgroup=c("TD", "LT"), compptile_lev25=c("low")), type = "response", re.form = ~0)

comp25_18_low <- comp25_18_low * 428
comp25_18_low

comp25_24_high <- predict(gam_age_group_comp25, newdata = data.frame(AGE= 24, LTgroup=c("TD", "LT"), compptile_lev25=c("high")), type = "response", re.form = ~0)

comp25_24_high <- comp25_24_high * 428
comp25_24_high

comp25_24_low <- predict(gam_age_group_comp25, newdata = data.frame(AGE= 24, LTgroup=c("TD", "LT"), compptile_lev25=c("low")), type = "response", re.form = ~0)

comp25_24_low <- comp25_24_low * 428
comp25_24_low

```

##Plot model results-comp 25th (Model 4)
```{r}

predict_comp25 <- (predict(gam_age_group_comp25, type = "response", se.fit = TRUE))
                   
Hebgrowth_gam$fit_comp25 <- predict_comp25$fit * 428
Hebgrowth_gam$fit_comp25_se <- predict_comp25$se.fit * 428

ggplot(Hebgrowth_gam, aes(y = fit_comp25, x = AGE, color = compptile_lev25, 
  linetype = LTgroup)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  geom_line(size = 1.3) +
  geom_ribbon(aes(ymin = fit_comp25 - fit_comp25_se, ymax = fit_comp25 + fit_comp25_se), fill = "grey", alpha = 0.2) +
  scale_linetype_manual(values = c("solid", "dotted")) +
  scale_color_manual(values = c("black", "dark grey"), labels = c("> 25th", "≤ 25th")) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=seq(12,24,1)) +
  ylim(0,350) +
  labs(
    x = "Age in months", 
    y = "Words \n produced \n (modeled \n estimate)", 
    linetype = "Expressive \nVocabulary \nGroup", color = "Receptive \nVocabulary \nGroup") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5, size = 16)) +
  theme(legend.title = element_text(size = 14))+
  theme(text = element_text(size = 16))
  
ggsave("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper/growthplot_comp_25.jpg", height = 8, width = 11, units = "in", dpi = 300)

```

# Add main effect of comp (50th) to age and group (model 6)
```{r}

gam_age_group_comp50 <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev50,
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  random = ~ 1 | CHILD_ID, 
                  data = Hebgrowth_gam)

summary(gam_age_group_comp50)

```
##Add age x group, age x comp, group x comp interactions (50th) Model 7
```{r}

gam_age_comp50_group_ageint <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev50 + pb(AGE, lambda = 10000) * LTgroup + pb(AGE, lambda = 10000)* compptile_lev50 + compptile_lev50 * LTgroup,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

summary(gam_age_comp50_group_ageint)

gam_age_comp50_group_age3way <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) * LTgroup * compptile_lev50,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam)

summary(gam_age_comp50_group_age3way)

```
##Comp50 x age interactions in TD and LT separately

```{r}

Hebgrowth_gam_LT <- Hebgrowth_gam %>%
  filter(LTgroup == "Lower")

gam_age_comp50_LT <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + compptile_lev50,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam_LT)

summary(gam_age_comp50_LT)

gam_age_comp50_LT_int <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) * compptile_lev50,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam_LT)

summary(gam_age_comp50_LT_int)


Hebgrowth_gam_TD <- Hebgrowth_gam %>%
  filter(LTgroup == "Higher")

gam_age_comp50_TD <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) + compptile_lev50,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam_TD)

summary(gam_age_comp50_TD)

gam_age_comp50_TD_int <- gamlss(prop_produced ~ pb(AGE, lambda = 10000) * compptile_lev50,
                  sigma.formula = ~pb(AGE, lambda = 10000),
                  family = BE, 
                  random = ~ 1 | CHILD_ID,
                  data = Hebgrowth_gam_TD)

summary(gam_age_comp50_TD_int)

```

## Get model fit values

```{r}

AIC(gam_age_group_comp50)
AIC(gam_age_comp50_group_ageint)
AIC(gam_age_comp50_group_age3way)

# Get BIC values

BIC(gam_age_group_comp50)
BIC(gam_age_comp50_group_ageint)
BIC(gam_age_comp50_group_age3way)

# Get Rsquared values

Rsq(gam_age_group_comp50)
Rsq(gam_age_comp50_group_ageint)
Rsq(gam_age_comp50_group_age3way)

# Compare models using liklihood ratio test

LR.test(gam_age_group, gam_age_group_comp50)
LR.test(gam_age_group_comp50, gam_age_comp50_group_ageint)
LR.test(gam_age_comp50_group_ageint, gam_age_comp50_group_age3way)

```
##Get predicted values by LT/TD group and comp (50th) at 18 and 24 months
```{r}

comp50_18_high <- predict(gam_age_comp50_group_ageint, newdata = data.frame(AGE= 18, LTgroup=c("Higher", "Lower"), compptile_lev50=c("Higher")), type = "response", re.form = ~0)

comp50_18_high <- comp50_18_high * 428
comp50_18_high

comp50_18_low <- predict(gam_age_comp50_group_ageint, newdata = data.frame(AGE= 18, LTgroup=c("Higher", "Lower"), compptile_lev50=c("Lower")), type = "response", re.form = ~0)

comp50_18_low <- comp50_18_low * 428
comp50_18_low

comp50_24_high <- predict(gam_age_comp50_group_ageint, newdata = data.frame(AGE= 24, LTgroup=c("Higher", "Lower"), compptile_lev50=c("Higher")), type = "response", re.form = ~0)

comp50_24_high <- comp50_24_high * 428
comp50_24_high

comp50_24_low <- predict(gam_age_comp50_group_ageint, newdata = data.frame(AGE= 24, LTgroup=c("Higher", "Lower"), compptile_lev50=c("Lower")), type = "response", re.form = ~0)

comp50_24_low <- comp50_24_low * 428
comp50_24_low

```
##Plot final comprehension model - FINAL 50th (Model 7)
```{r}

predict_comp50 <- (predict(gam_age_comp50_group_ageint, type = "response", se.fit = TRUE))
                   
Hebgrowth_gam$fit_comp50 <- predict_comp50$fit * 428
Hebgrowth_gam$fit_comp50_se <- predict_comp50$se.fit * 428

ggplot(Hebgrowth_gam, aes(y = fit_comp50, x = AGE, color = compptile_lev50, 
  linetype = LTgroup)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  geom_line(size = 1.3) +
  scale_linetype_manual(values = c("solid", "dotted")) +
  scale_color_manual(values = c("black", "dark grey"), labels = c("> 50th", "≤ 50th")) +
  geom_ribbon(aes(ymin = fit_comp50 - fit_comp50_se, ymax = fit_comp50 + fit_comp50_se), fill = "grey", alpha = 0.2) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=seq(12,24,1)) +
  ylim(0,350) +
  labs(
    x = "Age in months", 
    y = "Words \n produced \n (modeled \n estimate)", 
    linetype = "Expressive \nVocabulary \nGroup", color = "Receptive \nVocabulary \nGroup") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5, size = 16)) +
  theme(legend.title = element_text(size = 14))+
  theme(text = element_text(size = 16))
  
ggsave("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper/growthplot_comp_50.jpg", height = 8, width = 11, units = "in", dpi = 300)

```
#Not included in paper
##Descriptives of mean expressive vocabulary by age and group-Not included in paper
```{r}

Hebgrowth_desc <- Hebgrowth %>% group_by(LTgroup, AGE) %>%
  dplyr::summarize(
    n = n(),
    TotProd = mean(prod),
    SD = sd(prod),
    Minimum = min(prod),
    Maximum = max(prod)
  )


knitr::kable(
 Hebgrowth_desc,
  caption = "Table 2. Descriptive statistics for Words Produced by age and group.",
  note = "Maximum score possible = 404",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

```
##Plot of percentile levels by LT groups (same info as in Table 3)
```{r}

Hebgrowth_prod_plot <- ggplot(Hebgrowth, mapping = aes(x = adm, y = prod_centile_rank, fill = LTgroup)) + geom_boxplot()

Hebgrowth_prod_plot

Hebgrowth_comp_plot <- ggplot(Hebgrowth, mapping = aes(x = adm, y = comp_centile_rank, fill = LTgroup)) + geom_boxplot()

Hebgrowth_comp_plot

```
## getting EMMeans on predicted values - not included
```{r}
ggpredict(gam_age_group_int, terms = ~ LTgroup * AGE)
emmeans(gam_age_group, ~LTgroup + AGE)
```
