---
title: "Hebrew CDI Longitudinal Growth"
output: html_document
date: '2022-08-23; updated 2022-10-5; submitted 2024-05-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load libraries
```{r}

library(tidyverse)
library(effsize)
library(stargazer)
library(psych)
library(reghelper)
library(lme4)
library(lmerTest)
library(dplyr)
library(ggplot2)
library(sjPlot) #for plotting lmer and glmer mods
library(effects)
library(sjmisc)
library(sjstats) #use for r2 functions
library(gamlss)

```
#Load data.frame
```{r}

setwd("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper")

Hebgrowth <- read.csv("HebGrowth_data.csv", header = TRUE) %>%
    mutate(LTgroup = case_when(
              LTgroup == 0 ~ "TD",
              LTgroup == 1 ~ "LT"),
           Sex = case_when(
             Sex == "1" ~ "M",
             Sex == "2" ~ "F"))
           
Hebgrowth$LTgroup <- factor(Hebgrowth$LTgroup, levels = c("TD", "LT"))

Hebgrowth$Sex <- factor(Hebgrowth$Sex, levels = c("M", "F"))


Hebgrowth$adm <- factor(Hebgrowth$adm, levels = c("1", "2", "3"))
         

# Check data

Hebgrowth %>% 
  count(LTgroup)

Hebgrowth %>% group_by(adm, Sex, LTgroup) %>%
  count(age1)

Hebgrowth %>% group_by(adm, Sex) %>%
  count(AGE)

Hebgrowth %>% group_by(adm) %>%
  count(LTgroup)

Hebgrowth %>% group_by(compptile_lev) %>%
  count(LTgroup)

Hebgrowth %>% group_by(adm) %>%
  count(compptile_lev25)

Hebgrowth %>% group_by(compptile_lev25) %>%
  count(LTgroup)


```
#Descriptives of mean vocabulary by age and group
```{r}

Hebgrowth_desc <- Hebgrowth %>% group_by(LTgroup, AGE) %>%
  dplyr::summarize(
    n = n(),
    TotProd = mean(prod),
    SD = sd(prod),
    Minimum = min(prod),
    Maximum = max(prod)
  )


knitr::kable(
 Hebgrowth_desc,
  caption = "Table 2. Descriptive statistics for Words Produced by age and group.",
  note = "Maximum score possible = 404",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)


```
#Descriptives of prod and comp percentile by LT group
```{r}

Hebgrowth_desc_prodptile <- Hebgrowth %>% group_by(LTgroup, adm) %>%
  dplyr::summarize(
    n = n(),
    TotProdper = mean(prod_centile_rank),
    SD_prodp = sd(prod_centile_rank),
    Min_prodp = min(prod_centile_rank),
    Max_prodp = max(prod_centile_rank),
    TotCompper = mean(comp_centile_rank),
    SD_compp = SD(comp_centile_rank),
    Min_compp = min(comp_centile_rank),
    Max_compp = max(comp_centile_rank)
  )

knitr::kable(
 Hebgrowth_desc_prodptile,
  caption = "Descriptive statistics for Production and Comprehension Percentile by adm and group.",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)


Hebgrowth_prod_plot <- ggplot(Hebgrowth, mapping = aes(x = adm, y = prod_centile_rank, fill = LTgroup)) + geom_boxplot()

Hebgrowth_prod_plot

Hebgrowth_comp_plot <- ggplot(Hebgrowth, mapping = aes(x = adm, y = comp_centile_rank, fill = LTgroup)) + geom_boxplot()

Hebgrowth_comp_plot

```

#cross-tabs of prod percentile levels
```{r}

Hebgrowth %>% filter(adm == "1") %>%
  group_by(LTgroup, prod_centile_lev_adm2, prod_centile_lev_adm3) %>%
  count()

```

##Descriptives of comp percentile scores by LTgroup - 25th percentile

```{r}

# checking to make sure that group 1 compptile_lev25 is correct for all admins

Hebgrowth %>% group_by(adm) %>%
  count(compptile_lev25)

# looking at compptile group by LT group

Hebgrowth %>% group_by(LTgroup, adm) %>%
  count(compptile_lev25)

Hebgrowth_compptile25 <- Hebgrowth %>% group_by(compptile_lev25, adm) %>%
  dplyr::summarize(
    n = n(),
    Compptile = mean(comp_centile_rank),
    SD = sd(comp_centile_rank),
    Minimum = min(comp_centile_rank),
    Maximum = max(comp_centile_rank)
  )

knitr::kable(
 Hebgrowth_compptile25,
  caption = "Table x. Descriptive statistics for Words Understood percentile by group.",
  digits = 1,
  align = "lcccccc",
  escape = TRUE
)

```


## Growth models with GAMLSS (rather than LMER) production over age
```{r}

# Note GAMLSS models are specifically using the "beta" distribution family, which means they are bounded by 0 and 1 (like a logistic)

Hebgrowth$prod01 <- (Hebgrowth$prod+1)/428
Hebgrowth_gam <- na.omit(Hebgrowth)

#model 1 - age only

gam_age <- gamlss(prod01 ~ pb(AGE, lambda = 10000),
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

#model 2 - age and group main effects

gam_age_group <- gamlss(prod01 ~ pb(AGE, lambda = 10000) + LTgroup,
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

# model 3 - age and group main effects and interaction

gam_age_group_int <- gamlss(prod01 ~ pb(AGE, lambda = 10000) * LTgroup,
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

## Get summaries of models

summary(gam_age)
summary(gam_age_group)
summary(gam_age_group_int)

```

## Generate predicted values at 12, 18 and 24 months given the model
```{r}

predict(gam_age_group, newdata = data.frame(AGE= 12, LTgroup=c("LT", "TD")), type = "response", re.form = ~0)

predict(gam_age_group, newdata = data.frame(AGE= 18, LTgroup=c("LT", "TD")), type = "response", re.form = ~0)

predict(gam_age_group, newdata = data.frame(AGE= 24, LTgroup=c("LT", "TD")), type = "response", re.form = ~0)


# Get AIC values

AIC(gam_age)
AIC(gam_age_group)
AIC(gam_age_group_int)

# Get BIC values

BIC(gam_age)
BIC(gam_age_group)
BIC(gam_age_group_int)

# Get Rsquared values

Rsq(gam_age)
Rsq(gam_age_group)
Rsq(gam_age_group_int)

# Compare models using liklihood ratio test

LR.test(gam_age, gam_age_group)
LR.test(gam_age_group, gam_age_group_int)


```

## Plot model results - main effects only model
```{r}

Hebgrowth_gam$fitted <- (predict(gam_age_group, type = "response" ) * 428)

ggplot(Hebgrowth_gam, aes(y = fitted, x = AGE, linetype = LTgroup)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  geom_line(size = 1.1) +
  scale_color_manual(values=c("Black", "Grey")) +
  geom_point(aes(y = prod, shape = LTgroup), show.legend = F) +
  scale_shape_manual(values = c(16, 21)) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=seq(12,24,1)) +
  ylim(0,440) +
  labs(
    x = "Age in months", 
    y = "Words \n produced \n (modeled \n estimate)", linetype = "Group") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) +
  theme(text = element_text(size = 16))
  
ggsave("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper/growthplot.jpg", height = 8, width = 11, units = "in", dpi = 300)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# model 4 - Add main effect of comp to age and group
```{r}

gam_age_comp_group_alt25 <- gamlss(prod01 ~ pb(AGE, lambda = 10000) + LTgroup + compptile_lev25,
                  sigma.formula = ~pbm(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

summary(gam_age_comp_group_alt25)

```
#models 5 and 6 - adding age x comp and group x comp interations and 3 way
```{r}

gam_age_comp_group_agecompint25 <- gamlss(prod01 ~ pb(AGE) + LTgroup + (pb(AGE) * compptile_lev25) + (LTgroup * compptile_lev25),
                  sigma.formula = ~pb(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

summary(gam_age_comp_group_agecompint25)

## introducing 3-way interaction

gam_age_comp_group_3way25 <- gamlss(prod01 ~ pb(AGE) + LTgroup + compptile_lev25 + (pb(AGE) * compptile_lev25) + (pb(AGE) * compptile_lev25 * LTgroup),
                  sigma.formula = ~pbm(AGE),
                  family = BE, 
                  data = Hebgrowth_gam)

summary(gam_age_comp_group_3way25)

```
# Get model fit values

```{r}

AIC(gam_age_comp_group_alt25)
AIC(gam_age_comp_group_agecompint25)
AIC(gam_age_comp_group_3way25)

# Get BIC values

BIC(gam_age_comp_group_alt25)
BIC(gam_age_comp_group_agecompint25)
BIC(gam_age_comp_group_3way25)

# Get Rsquared values

Rsq(gam_age_comp_group_alt25)
Rsq(gam_age_comp_group_agecompint25)
Rsq(gam_age_comp_group_3way25)

# Compare models using liklihood ratio test

LR.test(gam_age_group, gam_age_comp_group_alt25)
LR.test(gam_age_comp_group_alt25, gam_age_comp_group_agecompint25)
LR.test(gam_age_comp_group_agecompint25, gam_age_comp_group_3way25)

```
##plot final comprehension model - FINAL- 25th
```{r}

Hebgrowth_gam$fitted <- (predict(gam_age_comp_group_alt25, type = "response" ) * 428)

ggplot(Hebgrowth_gam, aes(y = fitted, x = AGE, color = compptile_lev25, 
  linetype = LTgroup)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  geom_line(size = 1.3) +
  geom_point(aes(y = prod, shape = LTgroup, color = compptile_lev25), show.legend = F) +
  scale_linetype_manual(values = c("solid", "dotted")) +
  scale_color_manual(values = c("black", "dark grey"), labels = c("High", "Low")) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=seq(12,24,1)) +
  ylim(0,440) +
  labs(
    x = "Age in months", 
    y = "Words \n produced \n (modeled \n estimate)", 
    linetype = "Group", color = "Comprehension\nLevel") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5, size = 16)) +
  theme(legend.title = element_text(size = 16))+
  theme(text = element_text(size = 16))
  
ggsave("G:/Shared drives/Lang Learning Lab Management/Staff Personal/Active Staff Personal/VMarchman/mypapers/HebrewCDI/Growth Paper/growthplot_comp.jpg", height = 8, width = 11, units = "in", dpi = 300)
```

##predicting values - by LT group and comp level (25th)
```{r}

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 18, LTgroup=c("LT"), compptile_lev25=c("high")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 18, LTgroup=c("LT"), compptile_lev25=c("low")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 18, LTgroup=c("TD"), compptile_lev25=c("high")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 18, LTgroup=c("TD"), compptile_lev25=c("low")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 24, LTgroup=c("LT"), compptile_lev25=c("high")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 24, LTgroup=c("LT"), compptile_lev25=c("low")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 24, LTgroup=c("TD"), compptile_lev25=c("high")), type = "response", re.form = ~0)

predict(gam_age_comp_group_alt25, newdata = data.frame(AGE= 24, LTgroup=c("TD"), compptile_lev25=c("low")), type = "response", re.form = ~0)

```